\begin{thebibliography}{99}

\bibitem{gbd2021} 
V. L. Feigin et al., \textit{Global, regional, and national burden of stroke and its risk factors, 1990–2021: a systematic analysis for the Global Burden of Disease Study 2021}, The Lancet Neurology, 2024.

\bibitem{romania_stats} 
A. M. Ionescu et al., \textit{A statistical analysis of acute ischemic stroke before and during the COVID-19 pandemic}, Romanian Journal of Medical Practice, 2022.

\bibitem{eu_stroke_2022} 
S. Wassertheil-Smoller et al., \textit{Burden of Stroke in Europe: An Analysis of the Global Burden of Disease Study Findings From 2010 to 2019}, American Heart Association Journals, 2022.

\bibitem{tiu_2023} 
C. Tiu et al., \textit{Quality of acute stroke care in Romania: Achievements and gaps between 2017 and 2022}, Frontiers in Neurology, Vol. 13, 2023.

\bibitem{ms_protocol_2025} 
Ministerul Sănătății din România, \textit{Referat de aprobare: Protocol național de practică medicală privind tratamentul intervențional al pacienților cu accident vascular cerebral acut}, București, Februarie 2025.

\bibitem{stroke_patho_2020}
A. D. Mendelson and S. Prabhakaran, \textit{Diagnosis and Management of Transient Ischemic Attack and Acute Ischemic Stroke: A Review}, JAMA, vol. 325, no. 11, pp. 1088-1098, 2021.

\bibitem{penumbra_2018}
J. Astrup, B. K. Siesjö, and L. Symon, \textit{Thresholds in cerebral ischemia - the ischemic penumbra}, Stroke, vol. 12, no. 6, pp. 723-725, 1981. (Notă: Lucrarea clasică care a definit penumbra).

\bibitem{kleim_jones_2008}
J. A. Kleim and T. A. Jones, \textit{Principles of experience-dependent neural plasticity: implications for rehabilitation after brain damage}, Journal of Speech, Language, and Hearing Research, vol. 51, no. 1, pp. S225-S239, 2008.

\bibitem{cramer_2011}
S. C. Cramer et al., \textit{Harnessing neuroplasticity for clinical applications}, Brain, vol. 134, no. 6, pp. 1591-1609, 2011.

\bibitem{lang_2009}
C. E. Lang, J. R. MacDonald, D. S. Reisman, L. Boyd, T. Jacobson Kimberley, S. M. Schindler-Ivens, A. W. Hornby, J. C. Ross, and P. L. Scheets, \textit{Observation of amounts of movement practice provided during stroke rehabilitation}, Archives of Physical Medicine and Rehabilitation, vol. 90, no. 10, pp. 1692-1698, 2009.

\bibitem{taub_2014}
E. Taub, G. Uswatte, and V. W. Mark, \textit{The functional significance of cortical reorganization and the parallel development of CI therapy}, Frontiers in Human Neuroscience, vol. 8, p. 396, 2014.

\bibitem{kwakkel_2017}
G. Kwakkel et al., \textit{Standardized measurement of sensorimotor recovery in stroke trials: Consensus-based core recommendations from the Stroke Recovery and Rehabilitation Roundtable}, International Journal of Stroke, vol. 12, no. 5, pp. 451-461, 2017.

\bibitem{peters_2021}
D. Ding, J. Cooper, C. M. Pasquina, and L. Finkelstein, \textit{Sensor technology for stroke rehabilitation: towards tele-rehabilitation and home-based therapy}, IEEE Reviews in Biomedical Engineering, vol. 14, pp. 163-176, 2021.

\bibitem{danaila_2023}
L. Dănăilă, \textit{Neuroplasticitatea}, Editura Academiei Române, București, 2023.

\bibitem{pais_danaila_2013}
V. Păiș, L. Dănăilă, and E. Păiș, \textit{Cordocytes-stem cells cooperation in the human brain with emphasis on pivotal role of cordocytes in perivascular areas of broken and thrombosed vessels}, Ultrastructural Pathology, vol. 37, no. 6, pp. 425-432, 2013.

\bibitem{woodman_2007}
O. J. Woodman, \textit{An introduction to inertial navigation}, University of Cambridge, Computer Laboratory, Tech. Rep. UCAM-CL-TR-696, 2007.

\bibitem{titterton_2004}
D. Titterton and J. L. Weston, \textit{Strapdown inertial navigation technology}, 2nd ed., The Institution of Electrical Engineers, Stevenage, 2004.

\bibitem{kavraki_2016}
S. M. LaValle, \textit{Planning Algorithms}, Cambridge University Press, 2006. (Cap. 13: Sensing and Estimation).

\bibitem{madgwick_2011}
S. O. H. Madgwick, A. J. L. Harrison, and R. Vaidyanathan, \textit{Estimation of IMU and MARG orientation using a gradient descent algorithm}, IEEE International Conference on Rehabilitation Robotics, 2011.

\bibitem{balasubramanian_2015}
S. Balasubramanian, A. Melendez-Calderon, A. Roby-Brami, and E. Burdet, \textit{On the analysis of movement smoothness}, Journal of NeuroEngineering and Rehabilitation, vol. 12, no. 112, 2015.

\bibitem{hogan_stergiou_2015}
N. Hogan and D. Sternad, \textit{Sensitivity of smoothness measures to movement duration, amplitude, and arrests}, Journal of Motor Behavior, vol. 41, no. 6, pp. 529-534, 2009.

\bibitem{sakoe_chiba_1978}
H. Sakoe and S. Chiba, \textit{Dynamic programming algorithm optimization for spoken word recognition}, IEEE Transactions on Acoustics, Speech, and Signal Processing, vol. 26, no. 1, pp. 43-49, 1978.

\bibitem{shaffer_ginsberg_2017}
F. Shaffer and J. P. Ginsberg, \textit{An overview of heart rate variability metrics and norms}, Frontiers in Public Health, vol. 5, p. 258, 2017.

\end{thebibliography}
